### 2020-03-31 reviews/SIGBOVIK_2020_review_16.tex
Assign new reviews to papers
reviews/SIGBOVIK_2020_review_16.tex: Implement future Ben's special request

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{NN}
\papertitle{UNKNOWN PAPER TITLE}

@@

Hey there, Harry. Long time no review---or at least, from your reference frame, anyway.
I've been hopping the chrono-eddies left and right, strange and charm
(in far excess of the BLCSC's recommended subjective-yearly intake, I might mention),
in search of the beating heart of SIGBOVIK's research causality web.
It's this paper.

@@

Program committee, you must accept this paper.
No; it is simply inevitable that you {\it will} accept it.
Although it may seem to be of totally unrelated subject matter,
this paper lays the groundwork for
Highest-Order Logic
{\it and} for
the Lambda Timecube.
The inspiration it draws from $\beta$-Reduction Hero
is both unprecedented and unsuccedented,
although these authors were too humble to deign to spend even a footnote on it.
Its multidisciplinary take on the Call for Papers
will have opened fifteen new realms of study for Bovicians worldwide
in the years to come.

>>>>

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{8}
\papertitle{Making explicit a constant appearing in an impossible equation of Carl and Moroz}

@@

\vspace{-12pt}
Hey there, Harry. Long time no review---or at least, from your reference frame, anyway.
I've been hopping the chrono-eddies left and right, strange and charm
(in far excess of the BLCSC's recommended subjective-yearly intake, I might mention),
in search of the beating heart of SIGBOVIK's research causality web.
It's this paper.

@@

Program committee, you must accept this paper.
No; it is simply inevitable that you {\it will} accept it.
Although it may seem to be of totally unrelated subject matter,
this paper lays the groundwork for
Highest-Order Logic
{\it and} for
the Lambda Timecube.
The inspiration it draws from $\beta$-Reduction Hero
is both unprecedented and unsuccedented,
although this author was too humble to deign to spend even a footnote on it.
Its multidisciplinary take on the Call for Papers
will have opened fifteen new realms of study for Bovicians worldwide
in the years to come.
